### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@40755d0ee846afda73fd0e431f92d94208c395a1 🚀

introduction to the confusion matrix

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
65--98. \url{https://doi.org/10.1137/141000671}

>>>>

Binary classifiers are usually assessed by measuring properties of their
confusion matrix, \emph{i.e.} the contingency table reporting true/false
positive/negative hits. The same approach is used to evaluate
\emph{e.g.} species occurrence models (Allouche et al., 2006). A
confusion matrix is laid out as

\[\begin{pmatrix}
    \text{tp} & \text{fp} \\
    \text{fn} & \text{tn}
\end{pmatrix} \,,\]

wherein \(\text{tp}\) is the number of interactions predicted as
positive, \(\text{tn}\) is the number of non-interactions predicted as
negative, \(\text{fp}\) is the number of non-interactions predicted as
positive, and \(\text{fn}\) is the number of interactions predicted as
negative. Almost all measures based on the confusion matrix express
rates of error or success as proportions, and therefore the values of
these components matter in a \emph{relative} way.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Allouche2006AssAcc}{}%
Allouche, O., Tsoar, A., \& Kadmon, R. (2006). Assessing the accuracy of
species distribution models: Prevalence, kappa and the true skill
statistic (TSS). \emph{Journal of Applied Ecology}, \emph{43}(6),
1223--1232. \url{https://doi.org/10.1111/j.1365-2664.2006.01214.x}

\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
65--98. \url{https://doi.org/10.1137/141000671}
